Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-12 content/impl.tex
removing resultCC and resultEq

To summarize, Lemma~\ref{lem:sound} shows that the result $\resultCC$ of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
We have also shown in Lemma~\ref{lem:subsetifds} that the correlated-calls analysis improves the precision of the original IFDS result $\resultIFDS$, because the correlated-calls result $\resultCC$ underapproximates an equivalence-IDE result $\resultEq$.
Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result $\resultCC$ that is obtained when considering all receivers $R$.

>>>>

To summarize, Lemma~\ref{lem:sound} shows that the result of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
We have also shown in Lemma~\ref{lem:subsetifds} that for an IFDS problem $P$, the correlated-calls analysis improves the precision of the original IFDS result $\resultIFDS(P)$, because the correlated-calls result $\resultIDE(\transCC(P))$ underapproximates an equivalence-IDE result $\resultIDE(\transEq(P))$.
Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result that is obtained when considering all receivers $R$.
